Cost-effectiveness of a malaria elimination campaign

### 2017-03-09 paper.Rmd
more work on weather

# Create variables 
bes <- 
  bes %>%
  mutate(mda=ifelse(date<"2015-11-08", "pre_mda", 
                    ifelse(date<"2016-02-04", "mda", "post_mda")),
         intervention=district=="MAGUDE")

# Create model to estimate effectiveness
mod <-lm(p ~ mda*intervention + irs_coverage + age, data=bes, weights = population)
```

@@

```{r}
# Use model to predict conterfactual
other_irs <- bes %>% filter(year == 2016, district != "MAGUDE") %>% summarise(x =mean(irs_coverage, na.rm =TRUE)) %>% .$x
counter_factual <- 
   bes %>% filter(year == 2016, 
                  district == "MAGUDE")
results <- list()
for (i in 2016:2025){
  new_year <- counter_factual %>%
    mutate(year = i) 
  results[[i]] <- new_year
}
counter_factual <- bind_rows(results)
counter_factual$date <- 
  as.Date(paste0(counter_factual$year, substr(counter_factual$date, 5, 10)))

@@

@@

# Discussion

>>>>

# Create variables 
bes <- 
  bes %>%
  mutate(mda=ifelse(date<"2015-11-08", "pre_mda", 
                    ifelse(date<"2016-02-04", "mda", "post_mda")),
         intervention=district=="MAGUDE",
         magude = ifelse(district == 'MAGUDE', 'Magude', 'Not Magude'))

# Create model to estimate effectiveness
mod <-lm(pk ~ mda*intervention + irs_coverage, data=bes, weights = population)
```

@@

```{r}
# Use model to predict conterfactual
other_irs <- bes %>% filter(year == 2016, district != "MAGUDE") %>% summarise(x =mean(irs_coverage, na.rm =TRUE)) %>% .$x
counter_factual <- 
   bes %>% filter(year == 2016, 
                  district == "MAGUDE")
results <- list()
for (i in 2010:2020){
  new_year <- counter_factual %>%
    mutate(year = i) 
  results[[i]] <- new_year
}
counter_factual <- bind_rows(results)
counter_factual$date <- 
  as.Date(paste0(counter_factual$year, substr(counter_factual$date, 5, 10)))

@@

```{r}
x <- counter_factual
x$predicted <- predict(mod, x)
long <- gather(x, key, value, cases:predicted)
long$value <- as.numeric(long$value)
long <- long %>%
  mutate(value = ifelse(key == 'pk', NA, value))

y <- bes
long2 <- gather(y, key, value, cases:predicted)
long2$value <- as.numeric(long2$value)

z <- rbind(long %>%
             filter(year >= 2017),
           long2 %>%
             filter(year <= 2016))

ggplot(data = z %>%
         filter(key %in% c('predicted', 'pk'),
                district == 'MAGUDE'),
       aes(x = date,
           y = value,
           group = key,
           color = key)) +
  geom_line() +
  facet_wrap(~age)
```

@@

```{r}
x <- bes %>%
    filter(district != 'NAMAACHA') %>%
  # filter(district != 'MANHICA') %>%
  group_by(date,
           # year, month,
           # age, 
           magude) %>%
  summarise(#pk = weighted.mean(pk, w = population),
            cases = sum(cases),
            pop = sum(population),
            precip = mean(precip)) %>%
  ungroup %>%
  mutate(p = cases / pop * 1000) #%>%
  # mutate(date = as.Date(paste0(year, '-',
  #                              '06',
  #                              # month, 
  #                              '-01')))# %>%
  # filter(date >= '2014-07-01')

library(ggthemes)
library(cism)
ggplot(data = x,
       aes(x = date,
           color = magude,
           y = p)) +
  geom_line(alpha = 0.6) +
  # geom_smooth() +
  # facet_wrap(~age, ncol = 1) +
  # theme_bw()  +
  scale_color_manual(name = '',
                     values = c('blue', 'red')) +
  # theme_fivethirtyeight() +
  geom_vline(xintercept = as.numeric(as.Date(paste0(2010:2017, '-12-31'))),
             lty = 2, alpha = 0.2) +
  geom_vline(xintercept = as.numeric(as.Date(paste0('2015-03-15'))),
             color = 'darkgreen') +
  labs(x = 'Week',
       y = 'Weekly incidence per 1,000',
       title = 'Weekly clinical malaria',
       subtitle = 'Province of Maputo, all ages, weekly') +
  geom_label(data = data_frame(x = as.Date(paste0('2015-03-15')),
                               y = 15,
                               label = 'MDA'),
             aes(x = x,
                 y = y,
                 label = label),
             color = 'black') +
  theme_cism()
```
# Discussion

```{r}
bes <- bes %>% filter(district != 'NAMAACHA')
# Prediction
bes$predicted <- predict(mod, bes)

x <- bes %>%
    filter(district != 'NAMAACHA') %>%
  # filter(district != 'MANHICA') %>%
  group_by(date,
           # year, month,
           # age, 
           magude) %>%
  summarise(#pk = weighted.mean(pk, w = population),
            cases = sum(cases),
            pop = sum(population),
            precip = mean(precip),
            precip_risk = mean(precipitation_risk),
            predicted = mean(predicted)) %>%
  ungroup %>%
  mutate(p = cases / pop * 1000)
#%>%
  # mutate(date = as.Date(paste0(year, '-',
  #                              '06',
  #                              # month, 
  #                              '-01')))# %>%
  # filter(date >= '2014-07-01')

library(ggthemes)
ggplot(data = x,
       aes(x = date,
           color = magude,
           y = predicted)) +
  geom_line(alpha = 0.6) +
  # geom_smooth() +
  # facet_wrap(~age, ncol = 1) +
  # theme_bw()  +
  scale_color_manual(name = '',
                     values = c('blue', 'red')) +
  theme_fivethirtyeight() +
  geom_vline(xintercept = as.numeric(as.Date(paste0(2010:2017, '-12-31'))),
             lty = 2, alpha = 0.6) +
  geom_vline(xintercept = as.numeric(as.Date(paste0('2015-03-15')))) +
  geom_line(data = x,
            aes(x = date,
                y = p,
                color = magude),
                lty = 2,
            alpha = 0.5)

```

```{r}
# Precipitation
x <- bes %>%
  group_by(year, month) %>%
  summarise(p = mean(precipitation)) %>%
  mutate(date = as.Date(paste0(year, '-', month, '-01')))
ggplot(data = x,
       aes(x = date,
           y = p)) +
  geom_bar(stat = 'identity') 
```
